\documentclass[8pt,a4paper]{article}

\usepackage{atbegshi}
\AtBeginShipoutFirst{\special{pdf:tounicode EUC-UCS2}}


%空白の設定
\usepackage{geometry}
\geometry{left=20truemm, right=20truemm, top=15truemm, bottom=20truemm}


%行間の設定
\renewcommand{\baselinestretch}{1.1}

\makeatletter
\newcommand{\figcaption}[1]{\def\@captype{figure}\caption{#1}}
\newcommand{\tblcaption}[1]{\def\@captype{table}\caption{#1}}
\makeatother
%コマンドの定義
\newcommand{\pcl}{\partial}
\newcommand{\bsm}{\boldsymbol}
\newcommand{\bm}{\boldsymbol}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\udl}{\underline}

\usepackage[nottoc]{tocbibind} 
\usepackage{booktabs}
\usepackage[dvipdfmx]{graphicx}
\usepackage[dvipdfmx]{color}
\usepackage{amsmath, amssymb}
\usepackage{txfonts}
\usepackage{wrapfig}
\usepackage{ascmac}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{url}
\usepackage{color}
\usepackage{scalerel}
\usepackage{subfigure}
\usepackage{listings,jlisting}
\usepackage{comment}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{here}
\usepackage{verbatim}
\begin{comment}
\lstset{ 
basicstyle=\ttfamily\scriptsize,
  commentstyle=\textit,
  classoffset=1,
  keywordstyle=\bfseries,
  frame=tRBl,
  framesep=5pt,
  showstringspaces=false,
  numbers=left,
  stepnumber=1,
  numberstyle=\tiny,
  tabsize=2
}
\end{comment}

\definecolor{identifier}{rgb}{0.611, 0.862, 0.996}  % LightBlue (変数)
\definecolor{comment}{rgb}{0.415, 0.600, 0.333}     % DeepGreen (コメント)
\definecolor{keyword1}{rgb}{0.768, 0.521, 0.749}    % Purple    (予約語)
\definecolor{keyword2}{rgb}{0.862, 0.862, 0.666}    % Yellow    (関数名)
\definecolor{keyword3}{rgb}{0.2, 0.8, 1}            % Blue      (大域変数)
\definecolor{keyword4}{rgb}{0.854, 0.439, 0.839}    % Pink      (定数)
\definecolor{string}{rgb}{0.847, 0.560, 0.458}      % Orange    (文字列)

\lstset{
language={C},
backgroundcolor={\color[gray]{.85}},
basicstyle={\small\ttfamily},
identifierstyle={\small},
commentstyle={\small\ttfamily \color{comment}},
keywordstyle={\small\bfseries \color[rgb]{0,0,0.7}},
ndkeywordstyle={\small},
stringstyle={\small\ttfamily \color{keyword4}},
frame={tb},
breaklines=true,
columns=[l]{fullflexible},
numbers=left,
xrightmargin=0zw,
xleftmargin=3zw,
numberstyle={\scriptsize},
stepnumber=1,
numbersep=1zw,
morecomment=[l]{//}
}

\DeclareMathOperator*{\assem}{\scalerel*{\textsf{A}}{\sum}}
%\usepackage[refeq, refpage, japanese]{nomencl}
%\makenomenclature

\setcounter{tocdepth}{4}
\setcounter{secnumdepth}{3}
\newcommand{\todayd}{\the\year/\the\month/\the\day}


\begin{document} 

\begin{center}
	{\Large BBFE mlflowのマニュアル} \\
\end{center}

\rightline{\today}

本資料は有限要素法とレベルセット法を使用した二層流れ解析プログラムBBFE mlflowの解説資料であり、支配方程式・解法・ソースコード・実行手順・計算例を示す。

\tableofcontents

%\input{01_fluid}
\input{02_levelset}
\input{03_code}
%\input{04_cavity}
\input{05_dambreak}
\input{06_bubble}
\input{07_sloshing}

\begin{thebibliography}{99}
	\bibitem{Nagrath2003} Nagrath, S., Jansen, K. \& Lahey, R. T. Three Dimensional Simulation of Incompressible Two-phase Flows using a stabilized finite element method and level set approach. in vol. 56 KF.002 (2003)

	\bibitem{Matsumoto2006} 松本純一, 鈴木健 \& 手塚明. 気泡関数要素安定化法を用いた気液二相流解析. 混相流研究の進展 1, 181–188 (2006)

	\bibitem{Shi2019} Shi, J., Barriere, T., Liu, B. \& Cheng, Z. A simple and systematic scheme implemented in explicit FEM solver for surface tension effects in powder injection moulding process. Int. J. Mater. Form. 12, 123–134 (2019)

	\bibitem{Lo2005} Lo, D. C., Murugesan, K. \& Young, D. L. Numerical solution of three-dimensional velocity-vorticity Navier-Stokes equations by finite difference method. International Journal for Numerical Methods in Fluids vol. 47 1469–1487 Preprint at https://doi.org/10.1002/fld.822 (2005)

	% ３次元気泡
	\bibitem{Safi2017} Safi, M. A., Prasianakis, N. \& Turek, S. Benchmark computations for 3D two-phase flows: A coupled lattice Boltzmann-level set study. Comput. Math. Appl. 73, 520–536 (2017)

	\bibitem{Yamazaki2007} 山崎慎太郎, 西脇眞二, 泉井一浩 \& 吉村允孝. レベルセット法に基づく機械構造物の構造最適化. 日本機械学会論文集 C編 73, 72–79 (2007)
	\bibitem{Himeno1999} 姫野武洋 \& 渡辺紀徳. 微小重力環境における気液界面挙動の数値解析. 日本機械学会論文集 B編 65, 2333–2340 (1999)

	% Conservative LSM
	\bibitem{Olsson2005} Olsson, E. \& Kreiss, G. A conservative level set method for two phase flow. J. Comput. Phys. 210, 225–246 (2005)

	\bibitem{Olsson2007} Olsson, E., Kreiss, G. \& Zahedi, S. A conservative level set method for two phase flow II. J. Comput. Phys. 225, 785–807 (2007)

	\bibitem{Takeuchi2018} 竹内　一貴, 田中　満, 田尻　恭平, 西田　秀利, 二重解像度格子法を用いた保存型レベルセット法の有効性, 第 32 回数値流体力学シンポジウム, (2018), \url{https://www2.nagare.or.jp/cfd/cfd32/cfd32papers/paper/E10-3.pdf}

	\bibitem{Nakazawa2023} 中澤克成, 横嶋哲, 石川秀平 \& 久末信幸. レベルセット法とVOF法の基本性能評価: ACLS法，CICSAM法，THINC/WLIC法に注目して. 土木学会論文集 79, 22–00116 (2023)

	\bibitem{Pimenta2018} P. Pimenta, Level Set Implementation Using FEniCS, \url{https://public.allanswered.com/userfile/4156253533-1533592794457/Paulo___Levelset_Implementation.pdf}

	\bibitem{Shono2017} 生野 達大, 液圧ブロー成形のための大変形流体構造接触連成手法に関する検討, 平成28年度修士論文, \url{https://repository.dl.itc.u-tokyo.ac.jp/record/2003551/files/K-06442.pdf}

	% 体積保存の式の参考
	\bibitem{Tsubogo2003} 坪郷 浩一, 朝位 孝二, 羽田野 袈裟義, Level Set法を用いた気泡崩壊の数値計算に関する研究. 応用力学論文集 Vol.6, pp.201-208 (2003).
	\bibitem{Sussman1994} Sussman, M., Smereka, P. \& Osher, S. A Level Set Approach for Computing Solutions to Incompressible Two-Phase Flow. J. Comput. Phys. 114, 146–159 (1994)

	\bibitem{Yamaguchi2018} Yamaguchi, N. Finite element based level set method with various reinitializations for viscous incompressible two-phase (cid:13)ows. (2018)

	%% ２次元気泡(bubbleのcase1の履歴まで載っている)
	\bibitem{Mierka2016} Mierka, O. \& Turek, S. Numerical simulation of monodispersed droplet generation in nozzles. in Process-Spray 493–516 (Springer International Publishing, Cham, 2016).
	%% ２次元気泡(bubbleの速度履歴と形が載っている)
	\bibitem{Hysing2009} Hysing, S. et al. Quantitative benchmark computations of two‐dimensional bubble dynamics. Int. J. Numer. Methods Fluids 60, 1259–1288 (2009).
	%% ２次元気泡(bubbleの速度履歴と形が載っている)
	\bibitem{Klostermann2013} Klostermann, J., Schaake, K. \& Schwarze, R. Numerical simulation of a single rising bubble by VOF with surface compression. International Journal for Numerical Methods in Fluids 71, 960–982 (2013).

	%% ダムブレイクのV&V
	\bibitem{Okumura2009} 奥村弘 \& 丸岡晃. 自由界面問題に対する Semi-Lagrange Galerkin (SLG) 法の評価. 応用力学論文集 12, 155–162 (2009)

	\bibitem{Koshizuka1996} Koshizuka, S., \& Oka, Y. (1996). Moving-particle semi-implicit method for fragmentation of incompressible fluid. Nuclear science and engineering, 123(3), 421-434.

	\bibitem{Martin1952} Martin, J. C. \& Moyce, W. J. Part IV. An experimental study of the collapse of liquid columns on a rigid horizontal plane. Philos. Trans. R. Soc. Lond. 244, 312–324 (1952).

	%% スロッシング
	%% \bibitem{Himeno2023} https://www8.cao.go.jp/space/comittee/05-yuso/yuso-dai4/siryou3-1.pdf

	%% スロッシングの文献
	\bibitem{Okamoto1992} Okamoto, T. TWO-DIMENSIONAL SLOSHING ANALYSIS BY THE ARBITRARY LAGRANGIAN-EULERIAN FINITE ELEMENT METHOD. Structural Eng./Earthquake Eng 8, 207s–2216.

	\bibitem{Sakuraba2001} Sakuraba, M., Tanaka, S. \& Kashiyama, K. ALE parallel finite element analysis of non-linear free surface flows using PC cluster. J. Appl. Mech. 4, 113–120 (2001).
  
\end{thebibliography}

\end{document}

